### 2013-12-06 manuscripts/reply/short-reply.tex
Editing sections throughout `short-reply` ms.

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Biogeographers frequently seek to explain population and species
    differentiation on geographical phenomena.
    Establishing that a set of population splitting events occurred
    at the same time can be a potentially persuasive argument that a set of taxa
    are affected by the same geographic events.
    Unfortunately, estimating divergence times precisely when one lacks
    precise information about the rate of molecular evolution is a notoriously
    difficult problem in evolutionary biology.
    \citep{Huang2011} introduced an approximate Bayesian approach which can be
    used to estimate the probabilities of models in which multiple sets of taxa
    diverge at the same time. 
    This method (implemented in the software \msb) does not require a common
    set of character data that links all of the taxa under investigation, but
    does require the relative mutation rates among the taxa and loci to be
    assumed \emph{a priori}.
    Recently, \citet{Oaks2012} used this model-choice framework to 
    study 22 pairs of vertebrate lineages which are distributed across
    the Philippines; they also studied the behavior of the \msb approach
    using computer simulations.
    \citet{Oaks2012} found that the model was very sensitive to the 
    prior that is chosen and that the inference method had low power
    to detect variation in divergences times.
    These results were not surprising, in light of a rich statistical literature
    that shows that the marginal likelihood of a model is quite sensitive to the
    use of vague priors.
    Because this sensitivity to prior assumptions affects the crucial insights 
    that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
    that users of the approach should carefully assess the robustness of their 
    conclusions to different priors.
    According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
    was due to excessively broad priors on divergence times leading to 
    inadequate numbers of simulation replicates.
    They proposed a new model-averaging approach that uses narrow, empirically informed uniform
    priors.
    Here we demonstrate that the approach of \citet{Hickerson2013} is
    dangerous in the sense that the empirically-derived priors often
    exclude from consideration the true values of the models' parameters.
    On a more fundamental level, we question the value of adopting an 
    empirical Bayesian stance for this model-choice problem.
    The robust Bayesian approach of conducting analyses under a variety
    of priors can reveal prior sensitivity and communicate which assumptions
    underlie model inference.
    Furthermore, simulations provide insight into the temporal resolution of
    the method, which in turn helps guide appropriate interpretation of
    results.

@@

\newpage
\msb
\citep{Huang2011} uses approximate Bayesian computation (ABC) to
estimate the distribution of divergence times among co-distributed pairs of
taxa.
It approximates a posterior probability over models that range from a single
divergence-time parameter (i.e., simultaneous divergence of all pairs of taxa)
to the fully generalized model in which each pair of taxa diverged at a
unique time.
A full description of the model is given in \citet{Oaks2012}.
Frequently, the exact values of the divergence times are hard 
to determine because researchers typically lack precise knowledge 
of the rate at which substitutions occur.
So the exact divergence time is often viewed as a nuisance parameter, and
researchers focus on the number of divergence events.
The papers of \citet{Oaks2012} and \citet{Hickerson2013} are in agreement
on the fundamental methodological point about the model selection performed in \msb:
\begin{itemize}
   \item The use of vague priors on the divergence time parameters can lead to
       support models with few divergence events shared across taxa. Thus, the
       primary inference enabled by the approach is very sensitive to the
       priors on divergence times.
\end{itemize}

@@

In this paper, we discuss the potential theoretical and practical
considerations of using empirically informed priors for Bayesian model choice.
Furthermore, we evaluate the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different units of time, which makes the results
presented in their response difficult to interpret (see Supporting Information
for details).
Even when avoiding this error, we find their empirical Bayesian model-averaging
implementation of \msb remains biased toward clustered divergence models.
Furthermore, the approach provides another means by which the method can
``escape'' models with large parameter space, which manifests in the preference
of models that exclude from consideration the true values of the model's
parameters.
Our results, when combined with those of \citet{Oaks2012}, suggest that it is
difficult to choose a uniformly distributed prior on divergence times that is
broad enough to confidently contain the true values of parameters while being
narrow enough to avoid spurious support of models with less parameter space.
However, recent work shows more flexible probability distributions without a
hard upper bound (e.g., gamma) can accommodate prior uncertainty in divergence
times without inhibiting the marginal likelihoods of models with more
divergence-time parameters, and as a result, increase the method's power to
detect temporal variation in divergences
\citet{Oaks2014dpp}.

@@

These distinctions between Bayesian parameter estimation and model choice can
be illustrated with a simple example.
Let us say we are interested in the fairness of a particular coin, and we
denote the unknown probability of it landing heads as \myTheta{}.
More specifically, we are interested in the probability of two models, $M_1$
and $M_2$.
In both models the outcomes of flipping the coin are assumed to be binomially
distributed, but under $M_1$ the coin is weighted toward landing heads (i.e.,
$\myTheta{} > 0.5)$), whereas under $M_2$, the coin is weighted toward landing
tails (i.e., $\myTheta{} < 0.5$).
We already have data from flipping a different coin 20 times that landed both
heads and tails 10 times, and so we decide to use these data in specifying a
beta prior on fairness of the new coin of $beta(a=10, b=10)$
(Figure~\ref{figCoinFlip}).
We collect data by flipping the coin $N=10$ times, $y=3$ of which land heads.
Given the beta distribution is a conjugate prior for a binomial likelihood, the
posterior distribution has the nice analytical form $\theta \given y,N \sim
beta(a + y, b + N - y)$, which for the new dataset is simply $beta(13, 17)$
(Figure~\ref{figCoinFlip}).
The maximum a posteriori (MAP) estimate of the probability of heads is 0.429,
and following Equation~\ref{eq:marginallikelhiood} the marginal likelihoods of
our models of interest are
\begin{equation}
    p(y=3, N=10 \given M_1) = \int_{0.5}^{1} p(y=3, N=10 \given
    \myTheta{}, M_1)p(\myTheta{} \given M_1) d\myTheta{} \approx 0.029,
\end{equation}
and
\begin{equation}
    p(y=3, N=10 \given M_2) = \int_{0}^{0.5} p(y=3, N=10 \given
    \myTheta{}, M_2)p(\myTheta{} \given M_2) d\myTheta{} \approx 0.097.
\end{equation}
Given the models have equal probability under our prior, we can calculate the
posterior probability of Model 1 as
\begin{equation}
    p(M_1 \given y=3, N=10) = \frac{p(y=3, N=10 \given M_1)}{p(y=3, N=10 \given
    M_1) + p(y=3, N=10 \given M_2)} \approx 0.23.
\end{equation}
This is the correct posterior probability of Model 1 given our prior
and data.

@@

% \cwlnote{}{It seems like this section can be boiled down to ``empirical Bayes
%     approaches for model choice when using uniform priors can exclude the
%     $truth$ from the prior, which is a violation of Bayes theorem" or something
%     like that. Picking apart what they calculated and we calculated seems like
%     too much detail. I would try to simplify how this is being presented. This
%     can lead into how the use of more appropriate prior distributions should be
%     used.}
In addition to the theoretical concerns discussed above, there are practical
problems with using narrow, empirically informed, uniform priors for a method
that has already been shown to be biased toward models with less parameter
space.
The results of Hickerson et al.'s \citeyear{Hickerson2013} reanalysis of the
Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This is concerning, because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa, a major problem when
using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior
density (HPD) interval for the mean divergence time estimated under one of the
priors used by \citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the limit on the prior, because
some of the taxon pairs are expected to have diverged at times older than the
upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).
The strong preference for the questionable priors on divergence times (their
$M_1$ and $M_2$) in the model-averaged results of \citet{Hickerson2013} suggest
their approach is biased toward models with less parameter space, and as a
consequence, is biased toward estimating model-averaged posteriors dominated by
models that exclude true values of parameters of the model.
We explored this possibility in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging approach
of \citet{Hickerson2013}, but set one of prior models with a uniform prior on
divergence times that is unrealistically narrow, and almost certainly excludes
most, if not all, of the true divergence times of the 22 taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space, we expect \msb will preferentially sample from this
incorrect model yielding a posterior that is incorrect (i.e., the
model-averaged posterior will be dominated by an incorrect model that excludes
the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

@@

\subsection*{Additional thoughts on empirical priors in Bayesian model choice}
The preceding sections are not a general critique of Bayesian model averaging.
Rather, model averaging can provide an elegant way of incorporating
model uncertainty in Bayesian inference.
However, when averaging over models with narrow and broad uniform priors in
situations where the likelihood density is not expected to be uniformly
distributed, the posterior could be dominated by models that exclude from
consideration the true values of parameters due to the larger marginal
likelihoods of the models that are integrated over less space with high prior
weight yet low likelihood.

@@

\section*{Assessing the power of the model-averaging approach of
    \citet{Hickerson2013}}
While our results above clearly demonstrate the risks inherent to the empirical
Bayesian model-choice approach used by \citet{Hickerson2013}, one could justify
such risk if the method does indeed increase the power of the method and thus
decrease bias toward clustered divergence models.
We assess this possibility using simulation-based analyses to evaluate the power
of Hickerson et al.'s (\citeyear{Hickerson2013}) approach.
Following \citet{Oaks2012}, we simulated 1000 datasets with \divt{} for each of
the 22 population pairs randomly drawn from a uniform distribution, $U(0,
\divt{max})$, where \divt{max} was set to: 0.2, 0.4, 0.6, 0.8, 1.0, and 2.0, in
\globalcoalunit generations.
All other parameters were identically distributed as the prior.
We use the same $5\e6$ samples from the same set of five prior models as above
($M_1$, $M_2$, $M_3$, $M_4$, and $M_5$).
As described above, for each simulated dataset, we approximated the posterior
by retaining 1000 samples from the prior with the smallest Euclidean distance
from the true summary statistics.
In total, we analyzed 6000 replicate datasets, retaining 1000 model-averaged
posterior samples for each of them.

We find that the approach of \citet{Hickerson2013} struggles to estimate the
variance of divergence times (\vmratio{}) across most of the \divt{max}
we simulated, whether evaluating the unadjusted
(Figure~\ref{figPowerAccOmegaMedian}) or GLM-adjusted
(Figure~\ref{figPowerAccOmegaModeGLM}) posterior estimates.
The method only estimates \vmratio{} relatively well when the simulated
distribution of divergence times is identical to one of the prior models
(Figures~\ref{figPowerAccOmegaMedian}E \& \ref{figPowerAccOmegaModeGLM}E).
This is consistent with the findings of \citet{Oaks2012}  and
\citet{Hickerson2013} that \msb is highly sensitive to the prior distribution
deviating from the true, underlying distribution of the data.

@@

Looking at our simulation results in terms of the posterior probability of the
dispersion index of divergence times supporting the extreme case of one
divergence event (i.e., $p(\vmratio{} < 0.01 \given \ssSpace)$), we find the
method strongly supports one divergence in greater than 27\% of the replicates
across all the \divt{max} we simulated (Figure~\ref{figPowerOmegaProb}).
Following \citet{Hickerson2013}, we use a Bayes factor of greater than 10 as
the criterion for incorrect inference of a single divergence event.
By this criterion, there is strong support for a single divergence event in
more than 90\% of the replicates when divergences are random over the past
$2.4\globalpopsize$ generations, and more than 60\% when over the past
$3.2\globalpopsize$ generations or less (Figure~\ref{figPowerOmegaProb}).

Our results show that the empirical Baysian model-averaging approach leads to
spuriously strong support for the extreme case of a single divergence event
when populations diverged randomly over the last $8\globalpopsize$ generations.
To put this on the scale roughly consistent with a vertebrate mitochondrial
locus, assuming a mutation rate of $2\e{-8}$ per site per generation, this
translates to 5 million generations.
Assuming a mutation rate consistent with nuclear loci of $1\e{-9}$, this is 100
million generations.

@@

We find the model-averaging approach employing empirically informed uniform
priors lacks power to detect random variation in divergence times over a scale
of $8\globalpopsize$ generations or more, which roughly translates to millions
of generations for mitochondrial loci.
As a result, it is difficult to justify the risk of the approach to to exclude
regions of parameter space containing the truth.

%CWL: I would suggest removing this section
\section*{The use of power analysis to guide applications of \msb}
\citet{Hickerson2013} presented a power analysis of \msb under a narrow uniform
divergence-time prior of 0--1 coalescent units ago.
They found that under these prior conditions \msb can, assuming a
per-site rate of $1.92\e{-8}$ mutations per generation, detect multiple
divergence events among 18 taxa when the true divergences were random over
hundreds of thousands of generations or more.
\citet{Oaks2012} performed similar power analyses under three uniform
divergence-time priors as narrow as 0--5 coalescent units, and found the
method was able to detect multiple events among 22 when divergences were random
over millions of generations.
As recommended by \citet{Oaks2012}, it is important that investigators perform
power analyses to determine the method's power for their dataset, and decide if
\msb has sufficient power to address their hypotheses; in the case of the
Philippines dataset, it did not.
When doing so, it is important to consider what prior conditions are
relevant to their empirical system.
A divergence-time prior of 0--5 coalescent units is quite narrow considering
that this expresses the prior belief that all 22 taxon pairs diverged within
this window.
Certainly, it is a rare for there to be enough \emph{a priori} information to
be certain that all taxa diverged within the last 4$\globalpopsize$ generations
(i.e., 0--1 coalescent units).
Also, it seems unlikely that when such prior information is available that
being able to detect multiple divergences on the scale of hundreds of thousands
of generations will add much insight about the evolutionary history of the
taxa; assuming a rate of mutation consistent with nuclear loci ($1\e{-9}$),
this translates to a temporal resolution of 3 million generations or more.

@@

However, \citet{Hickerson2013} conclude that the bias is due to insufficient
prior sampling.
They argue the widest of the three priors used by \citet{Oaks2012} would
infrequently produce samples with many independent young divergence times.
However, their argument assumes the gene divergence times presented
in \citet{Oaks2012} were estimated without error.
These estimates were intended to only provide a very rough comparison of the
gene divergence times across the 22 taxa.
These analyses assumed an arbitrary strict mutation rate of $2\e{-8}$ for all
taxa, and are, of course, subject to estimation error.
Furthermore, the branch-length units of the gene trees are in millions of
years, whereas the divergence time prior of \msb is in generations, thus
\citet{Hickerson2013} make the implicit assumption that all 22 Philippine taxa
have a generation time of one year.
The argument of \citet{Hickerson2013} that divergence time estimates of
\citet{Oaks2012} ``should set an upper bound on their prior for \divt{}'' seems
questionable, especially given our findings presented above regarding the
behavior of \msb when empirically informed uniform priors are employed.

Even if we assume the gene divergence times are estimated without error,
Hickerson et al.'s \citeyear{Hickerson2013} argument only applies to one of the
three different priors used by \citet{Oaks2012}.
The narrowest prior on divergence times used by \citet{Oaks2012} ($U(0, 5
mya)$) closely mirrors the range of estimates of gene-divergence times.
Applying Hickerson et al.'s (\citeyear{Hickerson2013}) probability sampling
probability argument demonstrates this prior is densely populated with samples
with large numbers of divergence parameters with values younger than the
estimated gene divergence estimates.
Thus, if insufficient prior sampling is to blame for the bias, it should be
much reduced under the narrow prior on \divt{}.
However, the magnitude of the bias is very similar across all three priors
explored by \citet{Oaks2012}.
\citet{Hickerson2013} point out a case where the narrow prior performs
slightly better (panel L of Figures S32, S37, and S38 of \citet{Oaks2012}).
However, it is important to note that these results suffered from a bug
in \msb, and there are many cases after \citet{Oaks2012} corrected the 
bug where the narrow prior performs slightly worse (see panels D--J of
Figures 3 and S12).

To disentangle whether model likelihoods or insufficient prior sampling is to
blame for the method's spurious support for simple models, we must look at the
different predictions made by these two phenomena.
One example, as discussed by \citet{Oaks2012}, is that insufficient prior
sampling should create large variance among posterior estimates, and thus it
should cause analyses to be highly sensitive to the number of samples drawn
from the prior.
Furthermore, if the sampling error causes bias toward models with less
parameter space, as suggested by \citet{Hickerson2013}, we expect to see
support for these models decrease as sampling increases.
\citet{Oaks2012} do not see such sensitivity when they compare prior sample
sizes of $2\e6$, $5\e6$, and $10^7$.

>>>>

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Biogeographers frequently seek to explain population and species
    differentiation on geographical phenomena.
    Establishing that a set of population splitting events occurred
    at the same time can be a potentially persuasive argument that a set of taxa
    were affected by the same geographic events.
    Unfortunately, estimating divergence times precisely when one lacks
    precise information about the rate of molecular evolution is a notoriously
    difficult problem in evolutionary biology.
    \citep{Huang2011} introduced an approximate Bayesian approach which can be
    used to estimate the probabilities of models in which multiple sets of taxa
    diverge at the same time. 
    This method (implemented in the software \msb) does not require a common
    set of character data that links all of the taxa under investigation, but
    does require the relative mutation rates among the taxa and loci to be
    assumed \emph{a priori}.
    Recently, \citet{Oaks2012} used this model-choice framework to 
    study 22 pairs of vertebrate lineages which are distributed across
    the Philippines; they also studied the behavior of the \msb approach
    using computer simulations.
    \citet{Oaks2012} found that the model was very sensitive to the 
    prior that is chosen and that the inference method had low power
    to detect variation in divergences times.
    These results were not surprising, in light of a rich statistical literature
    that shows that the marginal likelihood of a model is quite sensitive to the
    use of vague priors.
    Because this sensitivity to prior assumptions affects the crucial insights 
    that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
    that users of the approach should carefully assess the robustness of their 
    conclusions to different priors.
    According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
    was due to excessively broad priors on divergence times leading to 
    inadequate numbers of simulation replicates.
    They proposed a new model-averaging approach that uses narrow, empirically informed uniform
    priors.
    Here we demonstrate that the approach of \citet{Hickerson2013} is
    dangerous in the sense that the empirically-derived priors often
    exclude from consideration the true values of the models' parameters.
    On a more fundamental level, we question the value of adopting an 
    empirical Bayesian stance for this model-choice problem.
    The robust Bayesian approach of conducting analyses under a variety
    of priors can reveal prior sensitivity and communicate which assumptions
    underlie model inference.
    Furthermore, simulations provide insight into the temporal resolution of
    the method, which in turn helps guide interpretation of results.

@@

\newpage
\msb
\citep{Huang2011} uses approximate Bayesian computation (ABC) to
estimate the distribution of divergence times among co-distributed pairs of
taxa.
It approximates a posterior probability over models that range from a single
divergence-time parameter (i.e., simultaneous divergence of all pairs of taxa)
to the fully generalized model in which each pair of taxa diverged at a
unique time.
A full description of the model is given in \citet{Oaks2012}.
Frequently, the exact values of the divergence times are hard 
to determine because researchers typically lack precise knowledge 
of the rate at which substitutions occur.
So the exact divergence time is often viewed as a nuisance parameter, and
researchers focus on the number of divergence events.
The papers of \citet{Oaks2012} and \citet{Hickerson2013} are in agreement
on the fundamental methodological point about the model selection performed in \msb:
\begin{itemize}
   \item The use of vague priors on the divergence-time parameters can lead to
       support models with few divergence events shared across taxa. Thus, the
       primary inference enabled by the approach is very sensitive to the
       priors on divergence times.
\end{itemize}

@@

In this paper, we discuss the potential theoretical and practical
considerations of using empirically informed priors for Bayesian model choice.
Furthermore, we evaluate the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different units of time, which makes the results
presented in their response difficult to interpret (see Supporting Information
for details).
Here, we avoid this error, but still find their approach to be biased toward
clustered divergence models.
Furthermore, the approach provides another means by which the method can
``escape'' models with large parameter space, which manifests in the preference
of models that exclude from consideration the true values of the model's
parameters.
Our results, when combined with those of \citet{Oaks2012}, suggest that it is
difficult to choose a uniformly distributed prior on divergence times that is
broad enough to confidently contain the true values of parameters while being
narrow enough to avoid spurious support of models with less parameter space.
However, recent work shows more flexible probability distributions without a
hard upper bound (e.g., gamma) can accommodate prior uncertainty in divergence
times without inhibiting the marginal likelihoods of models with more
divergence-time parameters, and as a result, increase the method's power to
detect temporal variation in divergences
\citet{Oaks2014dpp}.

@@

These distinctions between Bayesian parameter estimation and model choice can
be illustrated with a simple example.
Let us say we are interested in the fairness of a particular coin, and we
denote the unknown probability of it landing heads as \myTheta{}.
More specifically, we are interested in the probability of two models, $M_1$
and $M_2$.
In both models the outcomes of flipping the coin are assumed to be binomially
distributed, but under $M_1$ the coin is weighted toward landing heads (i.e.,
$\myTheta{} > 0.5)$), whereas under $M_2$, the coin is weighted toward landing
tails (i.e., $\myTheta{} < 0.5$).
We already have data from flipping a different coin 20 times that landed both
heads and tails 10 times, and so we decide to use these data in specifying a
beta prior on fairness of the new coin of $beta(a=10, b=10)$
(Figure~\ref{figCoinFlip}).
We collect data by flipping the coin of interest $N=10$ times, $y=3$ of which
land heads.
Given the beta distribution is a conjugate prior for a binomial likelihood, the
posterior distribution has the nice analytical form $\theta \given y,N \sim
beta(a + y, b + N - y)$, which for the new dataset is simply $beta(13, 17)$
(Figure~\ref{figCoinFlip}).
The maximum a posteriori (MAP) estimate of the probability of heads is 0.429,
and following Equation~\ref{eq:marginallikelhiood} the marginal likelihoods of
our models of interest are
\begin{equation}
    p(y=3, N=10 \given M_1) = \int_{0.5}^{1} p(y=3, N=10 \given
    \myTheta{}, M_1)p(\myTheta{} \given M_1) d\myTheta{} \approx 0.029,
\end{equation}
and
\begin{equation}
    p(y=3, N=10 \given M_2) = \int_{0}^{0.5} p(y=3, N=10 \given
    \myTheta{}, M_2)p(\myTheta{} \given M_2) d\myTheta{} \approx 0.097.
\end{equation}
Given the models have equal probability under our prior, we can calculate the
posterior probability of Model 1 as
\begin{equation}
    p(M_1 \given y=3, N=10) = \frac{p(y=3, N=10 \given M_1)}{p(y=3, N=10 \given
    M_1) + p(y=3, N=10 \given M_2)} \approx 0.23.
\end{equation}
This is the correct posterior probability of Model 1 given our prior
and data.

@@

% \cwlnote{}{It seems like this section can be boiled down to ``empirical Bayes
%     approaches for model choice when using uniform priors can exclude the
%     $truth$ from the prior, which is a violation of Bayes theorem" or something
%     like that. Picking apart what they calculated and we calculated seems like
%     too much detail. I would try to simplify how this is being presented. This
%     can lead into how the use of more appropriate prior distributions should be
%     used.}
In addition to the theoretical concerns discussed above, there are practical
problems with using narrow, empirically informed, uniform priors for a method
that has already been shown to be biased toward models with less parameter
space.
The results of Hickerson et al.'s \citeyear{Hickerson2013} reanalysis of the
Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This is concerning, because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa, a major problem when
using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior
density (HPD) interval for the mean divergence time estimated under one of the
priors used by \citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the limit on the prior, because
some of the taxon pairs are expected to have diverged at times older than the
upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).

The strong preference for the questionable priors on divergence times (their
$M_1$ and $M_2$) in the model-averaged results of \citet{Hickerson2013} suggest
their approach is biased toward models with less parameter space, and as a
consequence, is biased toward estimating model-averaged posteriors dominated by
models that exclude true values of parameters of the model.
We explored this possibility in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging approach
of \citet{Hickerson2013}, but set one of prior models with a uniform prior on
divergence times that is unrealistically narrow, and almost certainly excludes
most, if not all, of the true divergence times of the 22 taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space, we expect \msb will preferentially sample from this
incorrect model yielding a posterior that is incorrect (i.e., the
model-averaged posterior will be dominated by an incorrect model that excludes
the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

@@

\subsection*{Additional thoughts on empirical priors in Bayesian model choice}
The preceding sections are not a general critique of Bayesian model averaging.
Rather, model averaging can provide an elegant way of incorporating
model uncertainty in Bayesian inference.
However, when averaging over models with narrow and broad uniform priors on a
parameter with a likelihood density that is not expected to be uniformly
distributed, the posterior can be dominated by models that exclude from
consideration the true values of parameters due to the larger marginal
likelihoods of the models that are integrated over less space with high prior
weight yet low likelihood.

@@

\section*{Assessing the power of the model-averaging approach of
    \citet{Hickerson2013}}
While our results above clearly demonstrate the risks inherent to the empirical
Bayesian model-choice approach used by \citet{Hickerson2013}, one could justify
such risk if the method does indeed increase the power of the method and thus
decrease bias toward clustered divergence models.
We assess this possibility using simulation-based analyses.
Following \citet{Oaks2012}, we simulated 1000 datasets with \divt{} for each of
the 22 population pairs randomly drawn from a uniform distribution, $U(0,
\divt{max})$, where \divt{max} was set to: 0.2, 0.4, 0.6, 0.8, 1.0, and 2.0, in
\globalcoalunit generations.
All other parameters were identically distributed as the prior models.
As above, we generated a prior sample of $5\e6$ total samples from the five
prior models $M_1$, $M_2$, $M_3$, $M_4$, and $M_5$
(Table~\ref{tabModelChoiceEmpirical}).
For each simulated dataset, we approximated the posterior
by retaining 1000 samples from the prior with the smallest Euclidean distance
from the true summary statistics, as described above.
In total, we analyzed 6000 replicate datasets, retaining 1000 model-averaged
posterior samples for each of them.

We find that the approach of \citet{Hickerson2013} struggles to estimate the
variance of divergence times (\vmratio{}) across most of the \divt{max}
we simulated, whether evaluating the unadjusted
(Figure~S\ref{figPowerAccOmegaMedian}) or GLM-adjusted
(Figure~S\ref{figPowerAccOmegaModeGLM}) posterior estimates.
The method only estimates \vmratio{} relatively well when the simulated
distribution of divergence times is identical to one of the prior models
(Figures~S\ref{figPowerAccOmegaMedian}E \& S\ref{figPowerAccOmegaModeGLM}E).
This is consistent with the findings of \citet{Oaks2012}  and
\citet{Hickerson2013} that \msb is highly sensitive to the prior distribution
deviating from the true, underlying distribution of the data.

@@

Looking at our simulation results in terms of the posterior probability of the
dispersion index of divergence times supporting the extreme case of one
divergence event (i.e., $p(\vmratio{} < 0.01 \given \ssSpace)$), we find the
method strongly supports one divergence in greater than 27\% of the replicates
across all the \divt{max} we simulated (Figure~\ref{figPowerOmegaProb});
following \citet{Hickerson2013}, we use a Bayes factor of greater than 10 as
the criterion for incorrect inference of a single divergence event.
Furthermore, there is strong support for a single divergence event in
more than 90\% of the replicates when divergences are random over the past
$2.4\globalpopsize$ generations, and more than 60\% when over the past
$3.2\globalpopsize$ generations (Figure~\ref{figPowerOmegaProb}).

Our results show that the empirical Bayesian model-averaging approach leads to
spuriously strong support for the extreme case of a single divergence event
when populations diverged randomly over the last $8\globalpopsize$ generations.
To put this on the scale roughly consistent with a vertebrate mitochondrial
locus, assuming a mutation rate of $2\e{-8}$ per site per generation, this
translates to 5 million generations.
Assuming a mutation rate consistent with nuclear loci of $1\e{-9}$, this is 100
million generations.
Given the empirically Bayesian model-averaging approach of \citet{Hickerson2013}
lacks power to detect random variation in divergence times over such
timescales, it is difficult to justify the risk of the approach to exclude
regions of parameter space containing the truth.

@@

%CWL: I would suggest removing this section
\section*{The importance of power analysis to guide applications of \msb}
\citet{Hickerson2013} presented a power analysis of \msb under a narrow uniform
divergence-time prior of 0--1 coalescent units ago.
They found that under these prior conditions \msb can, assuming a
per-site rate of $1.92\e{-8}$ mutations per generation, detect multiple
divergence events among 18 taxa when the true divergences were random over
hundreds of thousands of generations or more.
\citet{Oaks2012} performed similar power analyses under three uniform
divergence-time priors as narrow as 0--5 coalescent units, and found the
method was able to detect multiple events among 22 when divergences were random
over millions of generations.
As recommended by \citet{Oaks2012}, it is important that investigators perform
power analyses to determine the method's power for their dataset, and decide if
\msb has sufficient temporal resolution to address their hypotheses; in the
case of the Philippines dataset, it did not.
When doing so, it is important to consider what prior conditions are
relevant to their empirical system.
A divergence-time prior of 0--5 coalescent units is quite narrow considering
that this expresses the prior belief that all 22 taxon pairs diverged within
this window.
Certainly, it is  rare for there to be enough \emph{a priori} information to
be certain that all taxa diverged within the last 4$\globalpopsize$ generations
(i.e., 0--1 coalescent units).
Also, it seems unlikely that when such prior information is available that
being able to detect multiple divergences on the scale of hundreds of thousands
of generations will add much insight about the evolutionary history of the
taxa; assuming a rate of mutation consistent with nuclear loci ($1\e{-9}$),
this translates to a temporal resolution of 3 million generations or more.

@@

However, \citet{Hickerson2013} conclude that the bias is due to insufficient
sampling.
They argue the widest of the three priors used by \citet{Oaks2012} would
infrequently produce samples with many independent population divergence times
as recent as the estimated gene divergence times presented in \citet{Oaks2012}.
However, this argument assumes the gene divergence times presented in
\citet{Oaks2012} were estimated without error.
These estimates were intended to only provide a rough comparison of the
gene divergence times across the 22 taxa.
These analyses assumed an arbitrary strict mutation rate of $2\e{-8}$ for all
taxa, and are, of course, subject to estimation error.
Furthermore, the branch-length units of the gene trees are in millions of
years, whereas the divergence time prior of \msb is in generations, thus
\citet{Hickerson2013} make the implicit assumption that all 22 Philippine taxa
have a generation time of one year.
The argument of \citet{Hickerson2013} that divergence time estimates of
\citet{Oaks2012} ``should set an upper bound on their prior for \divt{}'' seems
questionable, especially given our findings presented above regarding the
behavior of \msb when empirically informed uniform priors are employed.

Even if we assume the gene divergence times are estimated without error,
Hickerson et al.'s \citeyear{Hickerson2013} argument only applies to one of the
three different priors used by \citet{Oaks2012}.
The narrowest prior on divergence times used by \citet{Oaks2012} ($U(0, 5
mya)$) closely mirrors the range of estimates of gene-divergence times.
Applying Hickerson et al.'s (\citeyear{Hickerson2013}) sampling-probability
argument demonstrates this prior is densely populated with samples with large
numbers of divergence parameters with values younger than the estimated gene
divergence estimates.
Thus, if insufficient prior sampling is to blame for the bias, it should be
much reduced under the narrow prior on \divt{}.
However, the magnitude of the bias is very similar across all three priors
explored by \citet{Oaks2012}.
\citet{Hickerson2013} point out a case where the narrow prior performs
slightly better (panel L of Figures S32, S37, and S38 of \citet{Oaks2012}).
However, it is important to note that these results suffered from a bug
in \msb, and there are many cases after \citet{Oaks2012} corrected the 
bug where the narrow prior performs slightly worse (see panels D--J of
Figures 3 and S12).

To disentangle whether model likelihoods or insufficient prior sampling is to
blame for the method's spurious support for simple models, we must look at the
different predictions made by these two phenomena.
One example, as discussed by \citet{Oaks2012}, is that insufficient prior
sampling should create large variance among posterior estimates, and thus it
should cause analyses to be highly sensitive to the number of samples drawn
from the prior.
Furthermore, if sampling error is biased toward models with less
parameter space, as suggested by \citet{Hickerson2013}, we expect to see
support for these models decrease as sampling increases.
\citet{Oaks2012} do not see such sensitivity when they compare prior sample
sizes of $2\e6$, $5\e6$, and $10^7$.

To explore this prediction further, we repeat the analysis of the Philippines
dataset under the intermediate prior used by \citet{Oaks2012} ($\divt{} \sim
U(0, 10)$, $\meanDescendantTheta{} \sim (0.0005, 0.04)$, $\ancestralTheta{}
\sim (0.0005, 0.02)$), using a very large prior sample size of $10^8$.
When we look at the trace of the estimates of the dispersion index of
divergence times (\vmratio{}) as the prior samples accumulate
(Figure~\ref{figSamplingError}) we do not see the trend predicted by
\citet{Hickerson2013} in either the unadjusted or GLM-regression-adjusted
estimates.
While sampling error is always a reality, it does not appear to be playing a
large role in the results of \citet{Oaks2012} or presented above.
